Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-05 manuscript/response_to_reviews.Rmd

[*issue #71*](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/71)

Only assessing models with AIC is not enough to prove sound relationships in multidimensional and complex data-models. LL ratio tests or deviance-anova tests can be used in the case of nested models with LMM or GLMM respectively. Along the text: dAIC is generally referred as $\Delta$AIC, please change accordingly.

[*issue #94*](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/94)

**We have gone through the manuscript / tables and figures and updated where it said "dAICc" to be $\Delta$AICc. **

@@

- Line 231: define AICc. **This is done (with added reference)**

- *IM I'm a bit confused by the next three comments.*
- Line 234-247: it is not clear what the authors did, please explain clearer this paragraph and the next and why you did two different (yet similar) analyses (single-variable and full model).

- Line 241-242: enough to say once that models were selected based on AIC (line 237-238) and then one criterion, why dAIC<1 here and dAIC<2 before? The classic assumption is 2 (e.g. Burnham & Anderson 2004). See also my other comment above.

**We have modified the text here to read:
"Candidate variables were selected, based on the single-variable tests, as those that had a consistent direction of response across all droughts and whose addition to a corresponding null model improved fit (at $\Delta$AICc $\ge$ 1.0) in at least one drought year (Table 4). We note that the $\Delta$AICc $\ge$ 1.0 criterion is not a test of signficance, but of whether the variable has enough influence to be considered as a *candidate* variable in full models."**

### 2020-07-05 manuscript/climate_sensitivity_draft.Rmd
update candidate variable criteria in manuscript, respond to related reviewer concern
#95

We then determined the best full models for predicting $Rt$ for each individual drought year and for all years combined. Candidate variables were selected, based on the single-variable tests, as those whose addition to a corresponding null model improved fit (at $\Delta$AICc $\ge$ 1.0) in at least one drought year and had a consistent direction of response across all droughts (Table 4). We compared models with all possible combinations of candidate variables and identified the full set of models within $\Delta$AICc=1 of the very top model (that with lowest AICc), henceforth referred to as "full models". When a variable appeared in all top models and the sign of the coefficient was consistent across models, we viewed this as support for the acceptance/rejection of the associated prediction by the full models. If the variable appeared in only some of the models, we considered this partial support/rejection.

>>>>

We then determined the best full models for predicting $Rt$ for each individual drought year and for all years combined. Candidate variables were selected, based on the single-variable tests, as those that had a consistent direction of response across all droughts and whose addition to a corresponding null model improved fit (at $\Delta$AICc $\ge$ 1.0) in at least one drought year (Table 4). We note that the $\Delta$AICc $\ge$ 1.0 criterion is not a test of signficance, but of whether the variable has enough influence to be considered as a *candidate* variable in full models. We compared models with all possible combinations of candidate variables and identified the full set of models within $\Delta$AICc=1 of the very top model (that with lowest AICc), henceforth referred to as "full models". When a variable appeared in all top models and the sign of the coefficient was consistent across models, we viewed this as support for the acceptance/rejection of the associated prediction by the full models. If the variable appeared in only some of the models, we considered this partial support/rejection.
